\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{a4wide}
\bibliographystyle{ieeetr} % 'ieeetr' formats it in the standard IEEE computer science style


\title{Bachelor Thesis Proposal}
\author{Ruben Koelewijn \\ s1105300}
\date{\today}


\begin{document}

\maketitle

\section{Topic}
The topic of the planned research is to validate output from an automated concert newsletter. \footnote{https://n8n.albiobola.nl/form/738b1ccd-9f48-4f52-9d7d-ed7bdb0a2d30} An example can be found in the appendix.  This newsletter uses an LLM to scrape different concert venues in different cities, and compiles a list of the different acts. This LLM also generates a list of artists, genres and a summary, which can often contain mistakes. The goal of the research is to find out how to validate the output of the LLM by using real web-data and possibility how we can adapt this onto other AI Agents. 

\section{Methods}
To store and query the webdata, we will be using an Open Web Index \cite{hendriksen2026open} which stores the data in a standard, open source file format (Parquet). This reduces costs and resources, instead of using any other paid search API. 

\section{Timeline} 
Since I wish to graduate this semester, I will be starting the research from this week and hoping to finish this at the end of Q4, inline with the summer break. Weekly meetings with my supervisor have already been set up. 

\newpage
\section*{Appendix}
\begin{verbatim}
act: Brògeal
date: 2026-05-11
url: https://www.doornroosje.nl/event/brogeal/
venue: Merleyn
bands: Brògeal (main)
related_artists: The Pogues, Stiff Little Fingers, Proclaimers, The Smiths
genres: folk-punk, Celtic folk, pubrock
summary: The Scottish folk-punk band Brògeal from Falkirk performs an energetic mix of traditional Celtic influences and modern punk.

act: Ão
date: 2026-11-06
url: https://www.doornroosje.nl/event/ao/
venue: Merleyn
bands: Ão (main)
related_artists: Stromae, Rosalía, C. Tangana
genres: saudade, pop, folk, latin, electronic
summary: Belgian band Ão performs a bewitching mix of electronics, artpop, afropop, saudade, and alternative latin.

if you have any feedback on this service please do so here:
form feedback
Most of the text of each event is generated by a LLM and they do make mistakes. So if you spot a mistake in the text let me know so I can improve the content of the emails. Also if you have other suggestions on improving this service you can leave it at the above form.

---
This email was sent automatically with n8n
\end{verbatim}

\bibliography{references} 

\end{document}

