\chapter{Preliminaries}\label{preliminaries}
% This \emph{optional} chapter contains the stuff that your reader needs to know in order to understand
% your work.
% Your ``audience'' consists of fellow third year computing science bachelor students who have done the same
% core courses as you have, but not necessarily the same specialization, minor, or free electives.

% You do not have to call this chapter \emph{Preliminaries} and it does not need to be limited to one chapter.
% Some preliminary topics deserve their own chapter.
\noindent In this chapter, we introduce the concepts behind this thesis. First, we discuss the definitions of hallucinations in large language models. Secondly, we explain the subject of cross-lingual natural language interference and its relevance to this thesis. Lastly, we discuss knowledge graphs and its usage of non-parametric memory. 

\section{Hallucination in Large Language Models}\label{pre:sec:llm}
In this thesis, we will be discussing the occurrences of hallucinations in LLMs. LLMs are massive artificial neural networks
pre-trained on vast amounts of text data, designed to understand and generate human language. They show strong understanding in natural language and solving 
complex tasks \cite{zhao2023survey}. While these outputs often contain useful and correct information, they are prone to \textit{hallucinating}. 
Hallucination of a LLM consists of the model generating content that is not faithful to its source. Multiple types of hallucination exist, 
and following the taxonomy proposed by Huang \etal
\cite{huang2025survey}, we can categorise these into two types: 
\begin{itemize}
    \item \textbf{Factuality Hallucinations} 
    \\ Discrepancies between generated content and verifiable real-world facts. 
    This includes \textit{Fabrications} (made-up claims) and \textit{Contradictions} (statements that directly oppose reality).
    \item \textbf{Faithfulness Hallucinations} 
    \\ Divergence from the provided user input or context. This includes \textit{Instruction} (following the wrong instructions from the prompt), 
    \textit{Context} (Not understanding the context) and \textit{Logical} (Incorrect logic, e.g. math errors).  
\end{itemize}

\noindent Classifying the hallucinations allows us to have insight on what went wrong and where to improve, giving us the ability to do a system-level
diagnosis of the pipeline \cite{vinay2025failuremodesllmsystems}. For instance, a \textit{faithfulness} error indicates a failure to maintain ``context-boundary" stability \cite{vinay2025failuremodesllmsystems}, 
where a \textit{factuality} error might need validation by means of an external source. Because LLMs are often unable to faithfully detect their own factual errors 
  \cite{chen2023felm}, deterministic verification is required to ensure airtight verification. In our pipeline, we will be using the labels \texttt{INTRINSIC} for when a direct contradiction against the source was found, \texttt{EXTRINSIC} when were made up, but aren't a clear contradiction \cite{huang2025survey}. 

To understand why these factual hallucinations occur so frequently in localized domains like local music venues, we must look at how LLMs store information. LLMs encode knowledge within their network weights during pre-training, forming what is known as \textit{parametric memory} \cite{mallen2023when}. While parametric memory may be reliable for globally prominent entities (e.g., world-famous pop stars) due to their massive presence in the training data, it is inherently weak for niche, local entities. This limitation is known as \textit{popularity bias}. Kandpal \etal \cite{kandpal2023longtail} mathematically demonstrate that an LLM's ability to accurately recall a fact drops immensely for ``long-tail'' entities that appear infrequently in its training corpus. Consequently, when an LLM is tasked with summarizing text about a local grassroots band, it encounters a void in its parametric memory and is prone to hallucinating plausible, fabrications in-line with what it knows about other grassroots bands. 


\section{Cross-Lingual Natural Language Inference}\label{pre:sec:nli}
Natural Language Inference (NLI), also known as Recognizing Textual Entailment (RTE), 
is a core task in Natural Language Processing (NLP) \cite{conneau2020unsupervised}. 
NLP is a multidisciplinary field at the intersection between Computing Science, Linguistics, and Artificial Intelligence, where scientists focus on 
helping computers understand natural language. Common applications consist of machine translation, 
sentiment analysis, and automated summarisation. The latter is 
highly relevant for this thesis, since we deal with Information Extraction (IE), specifically
 extracting text and entities from websites \cite{gao2024empirical}, and Semantic Validation, 
 which involves logically validating the semantic meaning of different sentences to detect errors \cite{huang2025survey, chen2023felm}.

The task of NLI in NLP is determining the logical relationship between two pieces of text: 
a \textit{premise} and a \textit{hypothesis} \cite{conneau2020unsupervised}. Based on the truth of the premise, 
the model assigns one of three categorical labels as demonstrated in Table \ref{tab:nli_examples}:

\begin{table}[h]
    \centering
    \caption{Examples of Natural Language Inference (NLI) relationships.}
    \label{tab:nli_examples}
    \begin{tabular}{lll}
        \toprule
        \textbf{Premise} & \textbf{Hypothesis} & \textbf{NLI Label} \\
        \midrule
        Frank Boeijen is from Nijmegen. & Nijmegen is the hometown of Frank Boeijen. & \textit{Entailment} \\
        Frank Boeijen is from Nijmegen. & Frank Boeijen is from Amsterdam. & \textit{Contradiction} \\
        Frank Boeijen is from Nijmegen. & Frank Boeijen is coming back to Nijmegen. & \textit{Neutral} \\
        \bottomrule
    \end{tabular}
\end{table}

\begin{itemize}
    \item \textbf{Entailment:} The hypothesis is guaranteed to be true if the premise is true. In Table \ref{tab:nli_examples}, 
    the premise logically necessitates that Nijmegen is Boeijen's hometown \cite{conneau2020unsupervised}.
    \item \textbf{Contradiction:} The hypothesis is guaranteed to be false if the premise is true. 
    Since the premise establishes Nijmegen as the origin, a claim of Amsterdam constitutes a direct contradiction \cite{conneau2020unsupervised}.
    \item \textbf{Neutral:} The truth of the hypothesis cannot be determined from the premise alone. 
    While Frank Boeijen may be ``coming back" to Nijmegen, the original premise regarding his origin does not provide sufficient
     information to confirm or deny a return trip \cite{conneau2020unsupervised}.
\end{itemize}

\noindent In the context of this thesis, we utilize \textit{Cross-Lingual} NLI to bridge the language gap 
between Dutch source text and English generated summaries. By using a multilingual model like XLM-RoBERTa, 
we can evaluate a Dutch premise against an English hypothesis without an intermediate translation step,
 preserving the semantic nuances of the original concert metadata \cite{conneau2020unsupervised}.

\newpage
 \section{Knowledge Graphs and Non-Parametric Memory}\label{pre:sec:kg}
To counteract the unreliability and popularity bias of an LLM's internal parametric memory, modern NLP pipelines often integrate \textit{non-parametric memory}-external, deterministically structured databases \cite{mallen2023when}. A primary form of non-parametric memory is a Knowledge Graph (KG). 

A Knowledge Graph is an organized data structure that represents real-world entities as nodes (e.g., artists, venues, or albums) and the strict relationships between them as edges (e.g., ``originates from'' or ``performs genre''). Unlike parametric models, which recall facts via learned statistical associations that degrade for low-frequency entities, a KG retrieves facts through direct structured queries with deterministic outputs.

In order to replicate the pipeline structure with an integrated non-parametric for our niche local music knowledge, open-source databases such as MusicBrainz exist. The MusicBrainz database can be implemented as a knowledge graph, allowing us to cross-reference the generated claims against verified information. This option gives us the possibility to move on from ``Neutral" to a possible ``Contradiction'' when the source text does not provide enough context. 

\section{Binary Classification Metrics}
\label{sec:binary_metrics}
In Data Mining and Machine Learning, evaluating the performance of a classification model requires mapping its predicted class labels against the actual ground-truth labels. For a binary classification problem, instances are categorized into a positive class or a negative class. The results are summarized in a confusion matrix \cite{tan2019introduction}, which tabulates the outcomes into four fundamental categories:

\begin{itemize}
    \item \textbf{True Positive (TP):} The model correctly predicts the positive class.
    \item \textbf{True Negative (TN):} The model correctly predicts the negative class.
    \item \textbf{False Positive (FP):} The model incorrectly predicts the positive class (Type I error).
    \item \textbf{False Negative (FN):} The model incorrectly predicts the negative class (Type II error).
\end{itemize}

From these foundational counts, several theoretical metrics are derived to quantify different dimensions of the classifier's predictive performance.

\subsection{Accuracy, Precision, and Recall}
\textbf{Accuracy} is the most widely used metric and measures the overall proportion of correct predictions made by the model. However, accuracy can be a misleading indicator when the class distribution is highly unbalanced, as a classifier can achieve a high accuracy simply by predicting the majority class \cite{tan2019introduction}.
\begin{equation}
    \text{Accuracy} = \frac{TP + TN}{TP + TN + FP + FN}
\end{equation}

\noindent \textbf{Precision} evaluates the exactness of the classifier. It represents the fraction of records that actually belong to the positive class out of all the records the model classified as positive.
\begin{equation}
    \text{Precision} = \frac{TP}{TP + FP}
\end{equation}

\noindent \textbf{Recall} (also referred to as Sensitivity or the True Positive Rate) evaluates the completeness of the classifier. It measures the fraction of actual positive records that the model successfully detected.
\begin{equation}
    \text{Recall} = \frac{TP}{TP + FN}
\end{equation}

\subsection{F1-score and False Positive Rate}
Because classification models often face a trade-off between maximizing precision and maximizing recall, the \textbf{F1-score} (or F-measure) is used to combine both into a single metric. It is calculated as the harmonic mean of precision and recall. Using the harmonic mean instead of an arithmetic mean ensures that the metric heavily penalizes a model if either precision or recall is exceptionally low \cite{tan2019introduction}.
\begin{equation}
    \text{F1} = 2 \times \frac{\text{Precision} \times \text{Recall}}{\text{Precision} + \text{Recall}}
\end{equation}

\noindent Finally, the \textbf{False Positive Rate (FPR)} measures the proportion of actual negative instances that were falsely classified as positive. Tracking this metric is critical in cost-sensitive learning environments where committing a Type I error carries a significant penalty \cite{tan2019introduction}.
\begin{equation}
    \text{FPR} = \frac{FP}{FP + TN}
\end{equation}