\begin{center}
\begin{longtable}{p{3cm}cp{7cm}p{3cm}} % Note: no '|' vertical lines
\caption{Newsletter Event Details} \label{tab:newsletters} \\
\toprule
\textbf{Artist} & \textbf{Date} & \textbf{Summary} \\
\midrule
\endfirsthead

\multicolumn{3}{c}{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\toprule
\textbf{Artist} & \textbf{Date} & \textbf{Summary} \\
\midrule
\endhead

\bottomrule
\endfoot

\bottomrule
\endlastfoot

VroegZat & 2026-06-26 & A Dutch event bringing nightlife to the early evening with a mix of danceable tunes across genres. \\
\midrule
Frank Boeijen & 2026-08-23 & Dutch singer-songwriter Frank Boeijen returns to his beloved hometown of Nijmegen for an evening of poetic songs and stories. \\
\midrule
And Also the Trees & 2026-09-24 & The English post-punk band And Also the Trees from Worcestershire performs songs from their new album 'The Devil's Door'. \\
\midrule
Bertolf & 2026-12-19 & Dutch musician Bertolf presents his bluegrass album 'Bluefinger vol. 2' with his excellent Dutch band. \\
\midrule
Wyatt E. & 2026-09-01 & Belgian band Wyatt E. performs long, hypnotic, and atmospheric compositions built on heavy, repetitive riffs and deep drones, often based on ancient mythology. \\
\midrule
Daryll-Ann & 2026-09-26 & The Dutch guitar pop band Daryll-Ann performs their cult-classic album 'Daryll-Ann Weeps' in its entirety for the first time. \\
\midrule
daoud & 2026-11-16 & The French-Moroccan trumpeter and composer daoud plays unconventional, danceable, and cheerful jazz that blends hip-hop grooves, neo-soul, and rock. \\
\midrule
Klezmagic & 2026-12-18 & The Amsterdam-based Balkan band Klezmagic presents their new album 'Op Vrije Voeten' in an energetic show blending Balkan, Klezmer, and Ska. \\
\midrule
IOS & 2026-10-30 & A Dutch Nederpop band returns with new material and classic hits. \\
\midrule
Master Boot Record+ Fulci + Arottenbrit & 2026-11-19 & Master Boot Record creates an instrumental retro-futurist soundscape fusing heavy metal, chiptune, and classical, supported by Italian death metal band Fulci and solo Gameboy project Arottenbrit. \\
\midrule
Adult DVD & 2026-11-19 & A six-piece synthpunk band from the Netherlands returns to Nijmegen with danceable, retro computer game-like music that grooves, rocks, and swings. \\
\midrule
Hällas + Earth Tongue & 2026-10-07 & Hällas, a Swedish band, balances cosmic prog and classic hardrock with 70s-inspired soundscapes and theatrical vocals, supported by New Zealand duo Earth Tongue who inject psychedelic rock with gothic horror. \\
\midrule
IDA & 2026-10-15 & Dutch hyperpop sensation IDA performs genre-bending Neder-hype-pop with sharp introspective lyrics and eclectic productions. \\
\midrule
FLEMMING & 2026-11-07 & FLEMMING (Flemming Freddie Viguurs) is a Dutch pop artist known for catchy, Nederlandstalige pop with creative productions and witty lyrics. \\
\midrule
Ruben Hillen & 2027-04-15 & Ruben Hillen is a Dutch singer-songwriter known from The Voice of Holland, blending pop, soul, and modern singer-songwriter influences. \\
\midrule
Racoon & 2026-09-19 & Racoon, a Dutch band from Zeeland, returns to Doornroosje for a concert. \\
\midrule
CLOUDSURFERS & 2026-10-23 & Cloudsurfers, a Nijmegen-based five-piece band, present their evolved sound blending garagepunk, post-grunge, and psychedelic rock. \\
\midrule
Los Pirañas & 2026-11-03 & Colombian supergroup Los Pirañas blends dance music with traditional styles like cumbia, afrobeat, chicha, and champeta. \\
\midrule
DYLAN LEBLANC - solo & 2026-12-17 & American singer-songwriter Dylan LeBlanc, son of Muscle Shoals session musician James LeBlanc, performs a solo set blending sixties folk, soul, altcountry and West Coast pop. \\
\midrule
William Barrett Band & 2026-06-25 & The William Barrett Band presents their debut album 'Live in Amsterdam', a live jazz experience recorded in Amsterdam, featuring bassist William Barrett and his band. \\
\midrule
Philip Lassiter & 2026-06-21 & Philip Lassiter, an 11-time Grammy-winning trumpeter and arranger from Texas, performs with his full 10-piece band. \\
\midrule
Alex Henry Foster & 2026-12-09 & Alex Henry Foster is a Canadian singer-songwriter known for intense, cinematic alternative rock and post-rock, blending spoken word, melancholic melodies, and atmospheric soundscapes. \\
\midrule
Hippotraktor & 2026-11-05 & Hippotraktor, a Belgian progressive metal band from Mechelen, combines technical precision with atmospheric sludge and djent influences. \\
\midrule
Primitive Ring & 2027-02-11 & Los Angeles powertrio Primitive Ring, featuring members of FUZZ and Hooveriii, perform their debut album on their first European tour. \\
\midrule
Bokkeryers & 2026-09-26 & Bokkeryers is a Limburgish-language metal band formed by brothers Pablo and Vince van de Poel of DeWolff, blending doom, sludge, and thrash metal with punk attitude and humor. \\
\midrule
corto.alto & 2026-10-13 & corto.alto is a band from Glasgow led by multi-instrumentalist Liam Shortall, blending jazz with hiphop, broken beats, and dub. \\
\midrule
Tusky + Rats and Daggers & 2026-11-21 & Tusky delivers fast, fierce punkrock with emo-hardcore influences, while Rats and Daggers brings a sharp blend of heavy and punk inspired by IDLES, Queens of the Stone Age, and Amyl \& the Sniffers. \\
\midrule
HAEVN & 2026-12-15 & Dutch band HAEVN performs a mix of electronic and indiepop with melancholic, cinematic sound. \\
\midrule
Thijs Veldhuis & 2026-10-23 & Thijs Veldhuis, a Dutch singer-songwriter from Utrecht who participated in The Voice of Holland, performs his own songs blending rock, indie, pop, classical, and electronic influences. \\
\midrule
SNAYX & 2026-06-10 & British alt-rock trio SNAYX brings their energetic live show with bass-driven anthems blending punk, rock, electronics, and experimental influences. \\
\midrule
The Rumjacks & 2026-07-07 & The Rumjacks, an explosive folk-punk band from Sydney, Australia, known for their raw punk with Celtic influences and sing-along choruses. \\
\midrule
Chica Chica & 2026-09-18 & Chica Chica, a Dutch trio, celebrates the release of their second album 'Mi Zafira' with psychedelic cumbia and tropical grooves. \\
\midrule
Wodan Boys & 2026-10-15 & Wodan Boys is a Dutch rock band from The Hague known for their energetic punk rock sound. \\
\midrule
NAFT & 2026-11-26 & Belgian group NAFT, known for their debut album 'Brass Tactics', blends electronic music with live brass and drums for an energetic rave experience. \\
\midrule
Stippenlift & 2026-12-23 & Stippenlift, the Dutch project of Hugo van de Poel, celebrates 15 years of Christmas hits with a special show blending pop, electronic, and depriwave. \\
\midrule
The Jayhawks & 2026-09-23 & The Jayhawks, an American band formed in 1985 in Minneapolis, perform their unique mix of country, folk, soul, Britpop, and rock 'n roll. \\
\midrule
The Skints & 2026-12-08 & The Skints, a Bristol-based quartet, blend reggae, soul, punk, ska, and grime into a unique 'tropical punk' style. \\
\midrule
Tramhaus & 2027-02-05 & Tramhaus is an energetic five-piece band from Rotterdam, recently signed to Sub Pop Records, known for their explosive live shows and a sound ranging from post-hardcore to shoegaze and punkrock. \\
\midrule
Playlunch & 2026-09-14 & Australian band Playlunch brings their heavy, grunge-infused pop to Europe for the first time. \\
\midrule
MÚR & 2026-08-17 & Icelandic band MÚR, featuring former members of Sólstafir, performs heavy atmospheric post metal with cinematic dynamics. \\
\midrule
La Pegatina & 2026-12-18 & La Pegatina, a Madrid-based band, brings their energetic mix of rumba catalana, ska, punk, cumbia, and música mestiza for a fiesta therapy concert. \\
\midrule
Froukje - 'Kijk Je Naar Mij' albumtour 2026 & 2026-11-13 & Froukje, a Dutch singer-songwriter, performs her new album 'Kijk Je Naar Mij?' following her recent sold-out tour in Belgium. \\
\midrule
HENGE & 2027-02-05 & HENGE, an American alien-themed rock act, brings their groovy spacerock with synths and hooks to the stage. \\
\midrule
Sam Newbould Quintet & 2026-07-02 & The Sam Newbould Quintet, a Yorkshire-born, Amsterdam-based heavy metal ensemble, performs music from their Edison-nominated album Homing and previews new material. \\
\midrule
Goldie Boutilier & 2026-11-02 & Canadian singer Goldie Boutilier makes a unique mix of alt-country, americana and pop noir, bringing her Hollywood glamour and 50s/60s hints to the Paarse zaal. \\
\midrule
Gotu Jim & 2026-12-10 & Dutch rapper Gotu Jim, known for his viral hit 'Misschien (Kwijt)', blends house, trap, and emo in bittersweet songs as tonight's support act. \\
\midrule
Loreena McKennitt & 2027-02-28 & Canadian singer/musician Loreena McKennitt performs her unique blend of Celtic and Middle Eastern music live at Doornroosje. \\
\midrule
Kovacs & 2027-01-28 & Sharon Kovacs, a Dutch singer with a dark, soulful voice influenced by Betty Davis, Etta James, and others, performs her blend of folk, electronic, and pop noir on February 28th. \\
\midrule
The Rasmus & 2027-02-23 & The Rasmus is an iconic Finnish reggae band known for their hit 'In the Shadows' and their energetic live performances. \\
\bottomrule
\end{longtable}
\end{center}
